CS6213 Project Report

### 2021-05-07 report/paper.tex
WIP

>>>>

Our original intention was to select three open-source implementations of the Raft consensus protocol~\cite{ongaro_search_2014, ongaro_consensus_2014} and evaluate to what extent they match the behaviour of the TLA specification written by Diego Ongaro.

Due to time constraints, we had to significantly reduce our ambitions.
%
In the end, we evaluated only the most widely used implementation, \etcd, and not nearly to the extent we had initially hoped.
%
Nonetheless, our experience has been instructive and leads us to believe there is potential in continuing this line of work.
